Methods for Large Scale Learning to Rank

### 2014-03-10 report/Chapters/RelatedWork.tex
algemene inleiding related work

Section \ref{sec:lit_descr} describe the approaches on parallel or distributed Learning-to-Rank found in literature.
\section{Literature description}
\label{sec:lit_descr}

@@

\subsubsection{Boosting wrapped in Bagging}
Pavlov et al. \cite{Pavlov2010} at Yandex developed a hybrid model that combines two methods from ensemble learning: bagging and boosting. Bagging \cite{Breiman1996}, also called bootstrap aggregating, is a ensemble learning method in which $m$ training sets $D_1..D_m$ are constructed from the training set $D$ by uniformly sampling data items from $D$ with replacement. The bagging method is parallelisable by training each $D_i$ with $i \in \{1..m\}$ on a different node. Boosting \cite{Friedman2002} is an ensemble learning method in which multiple weak learners are iteratively added together into one ensemble model in such a way that new models focus more on those data instances that were misclassified before. Boosting is not parallelisable, but the authors state that learning a short boosted sequence on a single node is still a do-able task.\\

>>>>

Section \ref{sec:lit_descr} describe the approaches on parallel or distributed Learning-to-Rank found in literature.
\section{Literature description}
\label{sec:lit_descr}
Different approaches to parallelising Learning-to-Rank can be identified in literature. The following subsections describe the related work in the field categorised by approach.

@@

\subsubsection{Boosting wrapped in Bagging}
Pavlov et al. \cite{Pavlov2010} at Yandex developed a hybrid model that combines two methods from ensemble learning: bagging and boosting. Bagging \cite{Breiman1996}, also called bootstrap aggregating, is a ensemble learning method in which $m$ training sets $D_1..D_m$ are constructed from the training set $D$ by uniformly sampling data items from $D$ with replacement. The bagging method is parallelisable by training each $D_i$ with $i \in \{1..m\}$ on a different node. Boosting \cite{Friedman2002} is an ensemble learning method in which multiple weak learners are iteratively added together into one ensemble model in such a way that new models focus more on those data instances that were misclassified before. The boosting step itself is not parallelisable, but the authors state that learning a short boosted sequence on a single node is still a do-able task.\\

Ganjisaffar \cite{Ganjisaffar2011b} proposed a pairwise boosting-wrapped-in-bagging model called BL-MART, in contrast to BagBoo which is a pointwise model. BL-MART adds a bagging step to the LambdaMART \cite{Wu2008} ranking model, a model that uses the Gradient Boosting \cite{Friedman2002} ensemble method combined with regression tree weak learners. In contract to BagBoo, BL-MART is limited in the number of trees. An experiment on the TD2004 dataset resulted in 4500 trees using BL-MART while 1.1 million trees were created with the BagBoo model.
